Radio Emission from Red-Giant Hot Jupiters

### 2015-12-29 ms.tex
Edits to Introduction

Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}. 
Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim$1~mJy level, due to the small orbital distance of the planet and/or the larger planetary mass. 
\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed properties of stellar wind in the proximity of the stars. They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME). 
Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic fields based on \citet{christensen_et_al2009}.
We note that \revise{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.

@@

Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission. 
\revise{In addition, they considered the scenario where the post-bow shock heating could produce ionized hydrogen atoms. This indicates a configuration of radio wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit. }

In this paper, we \revise{consider another plausible scenario where} the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates compared to the previous result. 
\revise{In addition, two major updates from \citet{ignace2010} are the following.}
\revise{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
\revise{Second, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}

In Section \ref{s:assumptions}, we introduce the framework to obtain the frequency and the flux of planetary auroral radio emission, and describe our models for the stellar wind and planetary magnetosphere.
Section \ref{s:result} presents the estimates of the spectral radio flux of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
Section \ref{s:observability} gives the prospects for the signal detection with the current/future instruments. 
Estimates for the actual late-type (M type) evolved stars are also included. 
Finally, Section \ref{s:conc} concludes the paper with a brief summary.

>>>>

Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}. 
Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim$1~mJy level, due to the small orbital distance of the planet and/or the larger planetary mass. 
\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed properties of stellar wind in the proximity of the stars. They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME). 
Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic fields based on \citet{christensen_et_al2009}.
\revise{\citet{jardine2008} modeled reconnection between the magnetic field of a close-in planet and that of the host star to obtain estimates that are not based on the ``radiometric Bode's law''.}
Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.

@@

Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission. 
\revise{In addition, they considered a scenario in which post-bow shock heating could produce ionized hydrogen atoms. This indicates a configuration of radio-wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit.}

In this paper, we \revise{consider another plausible scenario where} the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates compared to the previous result. 
\revise{In addition, we introduce two major advances beyond the work of \citet{ignace2010} that are related to the observability of radio emission from RGHJs.}  % I don't like referring to our work as "updates" from Ignace
\revise{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detecting radio emission from RGHJs.
\revise{Second, we discuss the planetary parameter space to search for radio emission, employing scaling laws for the planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}

In Section \ref{s:assumptions}, we present the framework to obtain the frequency and the flux of planetary auroral radio emission, and describe our models for the stellar wind and planetary magnetosphere.
Section \ref{s:result} presents the estimates of the spectral radio flux of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
Section \ref{s:observability} gives the prospects for the signal detection with the current/future instruments. 
Estimates for the actual late-type (M type) evolved stars are also included. 
Finally, Section \ref{s:conc} concludes the paper with a brief summary.
